DATA 621 Homework #4

### 2019-11-04 hw4/HW4.Rmd
Update HW4

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(gridExtra)
library(dplyr)
library(Amelia)
library(kableExtra)
library(caret)
library(DMwR)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

```{r}
df <- read.csv('./data/insurance_training_data.csv') %>%
  mutate(TARGET_FLAG = as.factor(TARGET_FLAG))
evaluation <- read.csv("./data/insurance-evaluation-data.csv")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(dplyr)
library(Amelia)
library(kableExtra)
library(caret)
library(DMwR)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

```{r}
df <- read.csv('./data/insurance_training_data.csv') %>%
  mutate(TARGET_FLAG = as.factor(TARGET_FLAG)) %>%
  select(-INDEX)
evaluation <- read.csv("./data/insurance-evaluation-data.csv") %>%
  select(-INDEX)
```
